What is a Selection Coefficient?

### 2022-01-04 graphs_newt_snakes/What_is_sel_coef.Rmd
making new figures for sel coefs and trying to figure out how to bin the data

files <- list.files(path="~/Desktop/data", pattern="byind", full.names=TRUE, recursive=FALSE)
number=1
file <- read.table(files[number], header = TRUE)
file_name <- substr(files[number], 36, 168)
print(paste0("File Name: ", file_name))

@@

```{r, pheno fit graph log, warning = F}
graph_file<-file
title<-"Phenotype by Fitness"
subt<-file_name
    p <- ggplot(graph_file[which(graph_file$phenotype<=1001),], aes(phenotype, fitness)) +
    geom_point(colour = "darkred")+
    ggtitle(title, subtitle = subt) +
    #xlim(-1, 1000) +
    scale_x_log10()+
    theme_bw() + theme(legend.position="none")+
    # gganimate specific bits:
labs(title = 'Generation: {frame_time}', x = 'Phenotype (log)', y = 'Fitness') +
  transition_time(gen) +
  ease_aes('linear')
animate(p, duration = 30, fps = round(max(file$gen)/33), width = 400, height = 400, renderer = gifski_renderer())
anim_save("data/gganimate1_2log.gif")

@@

>>>>

files <- list.files(path="~/Desktop/data", pattern="byind", full.names=TRUE, recursive=FALSE)
number=7
file <- read.table(files[number], header = TRUE)
file_name <- substr(files[number], 36, 168)
print(paste0("File Name: ", file_name))

@@

```{r, pheno fit graph log, warning = F}
graph_file<-file
title<-"Phenotype by Fitness"
subt<-file_name
    p <- ggplot(graph_file[which(graph_file$phenotype<=1001),], aes(phenotype, fitness)) +
    geom_point(colour = "darkred")+
    ggtitle(title, subtitle = subt) +
    #xlim(-1, 1000) +
    scale_x_log10()+
    theme_bw() + theme(legend.position="none")+
    # gganimate specific bits:
labs(title = 'Generation: {frame_time}', x = 'Phenotype (log)', y = 'Fitness') +
  transition_time(gen) +
  ease_aes('linear')
animate(p, duration = 30, fps = round(max(graph_file$gen)/33), width = 400, height = 400, renderer = gifski_renderer())
anim_save("data/gganimate1_2log.gif")

@@

```{r, fitness and phenotype with gen bins}
graph_file<-file
graph_file$zone = "A"
graph_file[which(graph_file$gen > 100 & graph_file$gen < 199),]$zone="B"
graph_file[which(graph_file$gen > 200 & graph_file$gen < 299),]$zone="C"
graph_file[which(graph_file$gen > 300 & graph_file$gen < 399),]$zone="D"
graph_file[which(graph_file$gen > 400 & graph_file$gen < 499),]$zone="E"
graph_file[which(graph_file$gen > 500 & graph_file$gen < 599),]$zone="F"
graph_file[which(graph_file$gen > 600 & graph_file$gen < 699),]$zone="G"
graph_file[which(graph_file$gen > 700 & graph_file$gen < 799),]$zone="H"
graph_file[which(graph_file$gen > 800 & graph_file$gen < 899),]$zone="I"
graph_file[which(graph_file$gen > 900 ),]$zone="J"

title<-"1000gen Fitness, Color every 100gen"
subt<-file_name
    p <- ggplot(graph_file, aes(fitness, fill = zone)) +
    geom_histogram( bins = 50)+
    ggtitle(title, subtitle = subt) +
    #xlim(-1, 1000) +
    #scale_x_log10()+
    theme_bw()

p

title<-"1000gen Phenotype, Color every 100gen"
subt<-file_name
    p <- ggplot(graph_file, aes(phenotype, fill = zone)) +
    geom_histogram( bins = 50)+
    ggtitle(title, subtitle = subt) +
    #xlim(-1, 1000) +
    #scale_x_log10()+
    theme_bw()

p

```{r, phenotype bins}

graph_file<-file

pmin = min(file$phenotype)
pmax = max(file$phenotype)
psd = sd(file$phenotype)
pmean = mean(file$phenotype)

bin(file$phenotype)
graph_file$
